Designing a Search for the BBC

### 2013-08-28 coursework.tex
Fixed typo.
Very close to a first draft. Need to round off the evaluation and do some of the reshuffling of e.g. the first para of the design chapter then do a formal review.

\chapter{Design}

@@

@enduml
\end{comment}
\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\linewidth]{sequence_user.png}
  \end{center}
  \caption{Sequence diagram showing a user interacting with search\label{sequence-user}}
\end{figure}

@@

@enduml
\end{comment}
\begin{figure}[p]
  \begin{center}
    \includegraphics[width=\linewidth]{sequence_ajax.png}
  \end{center}
  \caption{Sequence diagram showing rich information lazy-loaded via AJAX\label{sequence-ajax}}
\end{figure}

@@

package Programmes {
class Programme
Programme <|-r- CreativeWork
class Brand extends Programme
class Series extends Programme
class Episode extends Programme

@@

@enduml
\end{comment}
\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{model.png}
  \end{center}
  \caption{Domain model for content items and other things pertinent to BBC contenet\label{model}}
\end{sidewaysfigure}

\chapter{Analysis}
\label{analysis}

\chapter{Evaluation}

>>>>

\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{rich-picture.png}
  \end{center}
  \caption{Rich Picture of the BBC search system\label{rich-picture}}
\end{sidewaysfigure}

\chapter{Design}
\label{design}

@@

@enduml
\end{comment}
\begin{figure}[p]
  \begin{center}
    \includegraphics[height=0.4\textheight]{sequence_user.png}
  \end{center}
  \caption{Sequence diagram showing a user interacting with search\label{sequence-user}}
\end{figure}

@@

@enduml
\end{comment}
\begin{figure}[p]
  \begin{center}
    \includegraphics[height=0.4\textheight]{sequence_ajax.png}
  \end{center}
  \caption{Sequence diagram showing rich information lazy-loaded via AJAX\label{sequence-ajax}}
\end{figure}

@@

package Programmes {
class Programme
Programme -r-|> CreativeWork
class Brand extends Programme
class Series extends Programme
class Episode extends Programme

@@

@enduml
\end{comment}
\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{model.png}
  \end{center}
  \caption{Domain model for content items and other things pertinent to BBC content\label{model}}
\end{sidewaysfigure}

\section{Discussion and Appraisal}
\label{appraisal}

The first question that should be asked is whether the problem
given has been solved as much as it can be. The problem of
a BBC-wide search application was predicted  --
and has certainly shown itself -- to be a very large-scale problem, the
full extent of which cannot be covered in this report. Thus it
is reasonable to conclude that the problem is not yet solved
at every level, but the high-level solutions are certainly promising.

The use case diagram is likely not complete and would need
a significant amount of user research and requirements-gathering
to collection all the possible use cases of the search system. It
is likely that the variations of the use cases are so numerous
that different diagrams exploring different combinations of use
cases should be made to replace the single one given. For instance,
very little has been touched on around user's seeking educational
and informative material such as GCSE Bitesize or any other
learning resouces.

The sequence diagram for the producer (or any other content creator)
indirectly getting their content into the seach system demonsrates
the need for asynchronous messaging (and publish-subscribe), but
the nuances of such a process are not comphrehensively shown in
this format. A better illutration for such a message-based integration
system might be derived from the illutrated patterns created
by Hohpe and Woolf. \cite{hohpe2004enterprise}

The behaviour of the query web application in figure~\ref{sequence-user}
is defined with a hard line
taken on keeping the information stored in the indexes to a minimum.
At a basic level, this is not unlike a \emph{content enricher} pattern
\cite{hohpe2004enterprise} whereby the search application
business layer enriches the stubs in the indexes with information
the source system (the index) simply does not have. At a more purist
extreme, this could follow a \emph{claim check} pattern where
the index returns only globally-unique identifiers for the matching
items and makes no attempt to present any other knowledge about them
(and thus avoids any synchronisation issues if an item is updated as
source).

The latter approach fully decouples the search indexes from any
deeper information -- leaving that responsbility to appropriate
source system -- but means that the raw, stub results are near useful
to an end user. This makes the AJAX-based alternative approach
in figure~\ref{sequence-ajax}
less of a desirable option (would a user really be presented a list
of URIs while some Javascript code replaces them one by one with
actual information?). Given the AJAX-driven behaviour appears
desirable in terms of responsiveness, it would seem that some trade-off
would need to happen in terms of what the indexes store as additional
information.

These decisions relate to how the system would implement the data model
in figure~\ref{model}. The onotology described is an aggregation
of several efforts by Raimond \cite{raimond2009bbc}, Rayfield
\cite{rayfield2011bbc} and others -- along with some additional work
to join them together -- to represent the wealth of
information with which the BBC deals. It could be argued both that
a search application that \emph{understands} this diversity of
content must reflect it in its domain model but that a search
application that is \emph{coupled} to the individual ontologies
in this way is brittle with regard to changes therein. Duplication
would only harm maintainability.

Thus the domain model given in figure~\ref{model} should only serve
as a communication artefact that leads to further development of
a domain model more suitable to the needs of the search application
without the need to maintain more than is necessary. The use
of \emph{subtype polymorphism} \cite{booch2007object} is likely
to be key to ensure the search domain model needs only use the APIs
it needs. For example, does the search application have a need
to differentiate between a \emph{NewsItem} and a \emph{BlogPost}
for the purposes of displaying the search result's title? If the
CreativeWork top-level class has a title property, then the domain
model so far to enable that one behaviour needs only one class!

The application could go further and interact via a single
SearchResult \emph{facade} \cite{fowler2002patterns} whose
instances provide appropriate responses to canonical hooks
such as \emph{getDisplayTitle()} and \emph{getDestinationUrl()}
via polymorphic \emph{composition} with different target classes
from the fuller domain model. Given that the search indexes
are likely to take in content from any number of future systems,
there is an appeal to taking a schemaless approach \cite{sadalage2012nosql}
and allow the search application's view layer to display
different kinds of results differently via \emph{duck typing}.
\cite{python2013ducktyping}

A dynamic, schema-free domain model used within the search application
-- noting that, of course, schemaless truly means there is an
implicit schema in the logic that creates these dynamic objects from
source systems \cite{sadalage2012nosql} -- could prove to aid the
search system's need to model different kinds of data in the same
index. For example, our designers might express a desire to put
small summaries of weather forecasts within search results that
contain places. In the static sense, we could say that anything
of \emph{Place} type is displayed with such a feature. With
a dynamic, duck-typed model, we could ask
``does this item have weather?'' in place of ``is this a place?'', thus
allowing for the future design that extends forecasts to football
matches (since football matches are \emph{Event}s that occur in
a \emph{Place}, it is reasonable for a weather property to be
set thereon).

Some of the advantages from duck-typing could be mirrored in
providing building the domain model around interfaces -- e.g.
\emph{class FootballMatch extends Event implements WeatherLocation} --
but it is still cumbersome to create such a large, static-typed
domain model that is used both at index time (in extracting the
information to build the indexes) and at query time (to understand
what item we have found and how to present it to the user).

Overall, we have some promising, high-level models from which to
start making such more fine-grained decisions about the search
application. The use cases are likely sufficient for early iterations
or a \emph{Minimal Viable Product} \cite{junk2000dynamic} and
the behaviours capture the overall needs of the system. There is still
much scope for returning to our systems thinking and Soft Systems
Methodology to monitor the general model for Checkland's ``3 Es''
(efficacy, efficiency and effectiveness) \cite{checkland1990soft},
which is only briefly touched on in my attempts to relate the
data model to the user's interaction with the system.

\chapter{Evaluation}
\ref{evaluation}

Overall, we have some promising, high-level models from which to
start making such more fine-grained decisions about the search
application. The use cases are likely sufficient for early iterations
or a \emph{Minimal Viable Product} \cite{junk2000dynamic} and
the behaviours capture the overall needs of the system. There is still
much scope for returning to our systems thinking and Soft Systems
Methodology to monitor the general model for Checkland's ``3 Es''
(efficacy, efficiency and effectiveness) \cite{checkland1990soft},
which is only briefly touched on in my attempts to relate the
data model to the user's interaction with the system.

The high-level nature of the modelling achieved has made it
difficult to meet any objectives over performance, latency or
robustness of software components involved. A BBC search application
needs to index news as it is published, serve millions of unique
visits every week and minimise potential for losing information. These
non-functional requirements are a challenge in their own right
and have not been met with the UML modelling presented.

This is not to say that UML is not capable as a tool for presenting
architecture around performance and resilience. It is perhaps
more appropriate to model and present some of these aspects through
component and deployment diagrams. Behaviour diagrams such as sequence
and activity do not suit well to showing timing or performance, although
a series of sequence diagrams could show how behaviour changes
in parts of the system to tolerate failure of certain components (e.g.
one component could be modelled to return from an internal cache if
a collaborator is returning temporary error status codes).

Even the models that are presented in this report do not paint the full
picture, but it could be argued that it is not their purpose to do so.
As stated at the end of section~\ref{appraisal}, the use case diagram
provides a starting point that might be sufficient for an early
iteration of a project in an \emph{Agile} methodology. \cite{beck2001manifesto}

An Agile approach to developing the search application could distill
the use cases even further and shape the requirements to the rest
thereof later in the development process based on feedback and reacting
to changes. A similar approach would allow us to start with the smaller
domain model also discussed in section~\ref{appraisal} and allow it to grow
to the necessary size to need -- i.e. we can defer the decision of ``how big
should the domain model be?'' until we are at a point where we have more
information to answer that (at which point we would hope it is as comprehensive
as is necessary to support the application currently running and no more).

Thus even if the use case and domain models are not as comprehensive or
as honed as they need to be to build the entire application, they serve
their purpose adequately to communicate the first iterations of
development or -- especially in the case of the domain model -- information
pertaining to the whole organisation, even if only small parts of it are
they modelled directly in the application being built.

The sequence diagrams seemed to provoke more debate of the merits of
returning rich information in a single response versus an AJAX-driven
approach (or some trade-off in between). Again, I would emphasise the
communication aspect UML modelling and argue that encouraging such debate
is a successful application of UML, not a failure because a decision
has not been made between two designs at this early stage.

Some of this hints at drawback of UML modelling being that it encourages
a lot of design decision at an early stage -- stage at which we arguably
have the least information. \cite{kelly2013conway} There are plenty of
efforts in spite of this that promote modelling and UML being used
compatibly within an Agile process. The use of other modelling techniques
in an Agile setting such as
Rational Unified Process (RUP) and Agile Unified Process (AUP) are described by
Ambler. \cite{ambler2002agile} It may have been more suitable to incorporate
a more diverse range of modelling techniques in the design and analysis
presented so as to find the true strengths of each respective approach.
